\section{The Pulsar/\glslink{PWN}{Pulsar Wind Nebulae} System}

Describe pulsar/PWN/SNR system:

\begin{itemize}
  \item Describe how a supernova creates an SNR and leaves behinda
    a pulsar wind nebula. 
  \item ``Pulsars are now known to be created in Supernova events,
    where the dense stellar core created in thermonuclear reactions is
    left over after the nova event. Depending on its mass, the remaining
    solar core may form a neutron star or a black hole. The determining
    criterion is the Chandrasekhar limit (MCh) given by:'' -- dalton\_2011\_identication-gamma-ray
\end{itemize}

\subsection{Pulsar Properties}

\todo[inline]{XXXXXXXXXXXXXXXX}

% Good discussion of PWN physics with some simple formulas: 
%   ``The Evolution and Structure of Pulsar Wind Nebulae''
%   Bryan M. Gaensler and Patrick O. Slane


% good discussion of radius of termination shock in: kargaltsev_2008_pulsar-nebulae

% Another review paper (looks to describe pulsar modeling):
%  ``High Energy Studies of Pulsar Wind Nebulae''
%     Patrick Slane

% Also, Adam Van Etten's thesis: 1.1 Pulsar Wind Nebula Structure

% Good reference: ``Carroll and Ostlie'' page 593

% good refernce on PWN physics: \cite{fuste_2007_g-ray-observations}

\begin{itemize}
  \item ``Following this discovery, a theoretical understanding was
  soon developed in which the central pulsar generates a magnetized
  particle wind, whose ultrarelativistic electrons and positrons radiate
  synchrotron emission across the electromagnetic spectrum (Pacini \&
  Salvati 1973, Rees \& Gunn 1974). The pulsar has steadily released
  about a third of its total reservoir of ???? ergs
  of rotational energy into its surrounding nebula over the last 950
  years. This is in sharp contrast to shell-like SNRs, in which the
  dominant energy source is the ??? ergs of kinetic energy
  released at the moment of the original SN explosion.''  -- \cite{gaensler_2006_evolution-structure}
  \item 
    % described in Adam Van Etten's thesis
    What is terminaltion shock of PWNe.
  \item 
    How is pulsar outflow accelerated at shock?
\end{itemize}


\todo[inline]{Find a plot of a rotating pulsar. The simplest
rotating dipole model}

The energy powering pulsars and \glspl{PWN} is comonly
believed to originate in rotational kintetic energy stored in
the netutron star. 
Both the period \period and the period derivative
$\perioddot=d\period/d\time$ can be directly observed for a pulsar
and typically the pulsar is slowing down (\perioddot<0).
We write the rotational kinetic energy as
\begin{equation}
  \energyrotational = \tfrac{1}{2} I \angularfrequency^2
\end{equation}
where $\omega = 2\pi/\period$ and \period is the period of
rotation of the pulsar. We make the conection between
the pulsar's spin-down energy and the rotational kintecit energy as
$\energydot = - \derivative\energyrotational/\dtime$

The rotational kinetic energy in a pulsar can be written as
\begin{equation}
  \energydot = 4\pi^2 \momentofinertia \perioddot/\period^2,
\end{equation}
where \momentofinertia is the moment of inertia.
For a uniform sphwere,
\begin{equation}
  \momentofinertia = \frac{2}{5} M R^2
\end{equation}
Pulsars are assumed to be uniform spheres with $R=10\unitspace\km$
and $M=1.4\solarmass$, which leads to a canonical moment of inertia of
$\momentofinertia=10^{45}\unitspace\gram\cm^{-2}$.

It is believed that as the pulsar spins down, the this rotational energy
is released as pulsed electromagnetic radiation and also as a wind of
electrons and positrons accelerated in the magnetic field of the pulsar.

As the pulsar slows down, it released the rotational kinetic energy
\begin{equation}
  \energydot = - \frac{4 \pi^2 \momentofinertia \perioddot}{\period^3}
\end{equation}
where \perioddot is the rate of decrease in the period of the pulsar.

\todo[inline]{Discuss uniform dipole model}

We conventionally assume that the period and period derivative are related
by the equation
\begin{equation}\eqnlabel{angular_frequency_derivative_relation}
  \angularfrequencydot \propto \angularfrequency^\breakingindex
\end{equation}
where $\angularfrequency=2\pi/\period$, and $\breakingindex$
is the pulsar breaking index. 

\begin{itemize}
  \item ``though n has only been confidently measured for five pulsars,
  in each case falling in the range 2 < n < 3 (Livingstone et al. (2007)
  and references therein).'' -- Adam Van Etten's thesis
\item ``The braking index is the power to which the slowdown in angular
velocity occurs, and is defined as:
  \begin{equation}
    n = \frac{\period \perioddotdot}{\perioddot} + 2
  \end{equation}
  '' -- keogh\_2010\_search-pulsar
\end{itemize}

Equation \eqnref{angular_frequency_derivative_relation} is
a Bernoulli differential equation which can be integrated to solve for time

\begin{equation}
  T = \frac{\period}{(\breakingindex-1) |\perioddot|}
  \left(
  1-\left(\frac{\period_0}{\period}\right)^{(\breakingindex-1)}
  \right)
\end{equation}

\begin{itemize}
  \item TODO: cite Manchester \& Taylor 1977
\end{itemize}



\begin{equation}
  \pulsarage = \period/2\perioddot
\end{equation}


\begin{itemize}
  \item What is a typical moment of inertia, typical dE/dT
  \item What fraction of pulsar energy is released observationally
\end{itemize}

\subsection{Pulsar Magnetosphere}

\subsection{Pulsar Wind Nebulae}

\begin{itemize}
  \item Discuss termination shock (i.e. section 3.3.2 of dalton\_2011\_identication-gamma-ray
  \item The radius of the termination shock is
    \begin{equation}
      \radiusterminationshock = \sqrt{\frac{\energydot}{\tfrac{4}{3}\pi \pressureISM \speedoflight}}
    \end{equation}

\end{itemize}

\todo[inline]{Discuss pulsar evolution ``The Evolution and Structure of
Pulsar Wind Nebulae'' -- Bryan M. Gaensler and Patrick O. Slane}

\todo[inline]{Describe Mattana's work on PWNe: ``On the evolution of
the Gamma- and X-ray luminosities of Pulsar Wind Nebulae''}

