\prefacesection{Acknowledgement}

This thesis was made possibly only by the incredible support and
mentorship of a large number of teachers, advisers, colleagues, and
friends.

I would first like to acknowledge the educational institutes which taught
me physics: my high school HB Woodlawn, my undergraduate institution
Marlboro College, and my research university Stanford University.  At HB
Woodlawn, I acknowledge Mark Dodge, my high school physics teacher, who
sparked my initial interest in physics. At Marlboro College, I would like
to thank the professors Travis Norsen, Matt Ollis, and Jim Mahoney who
sparked my interests in math and science.

I would next like to acknowledge the science advisers who brought the
science I was learning in my textbooks to life.  These people are Ron
Turner at ANSER, Tony Tyson at UC Davis, and Apurva Mehta and Sam Webb
at SLAC.

During my PhD I was helped by an almost overwhelmingly large number
of people in the \gls{LAT} collaboration.  These include Damien Parent,
David Smith, Heather Kelly, James Chiang Jean Ballet Joanne Bogart, Johann
Cohen-Tanugi Junichiro Katsuta, Marianne Lemoine-Goumard, Marie-H\'el\`ene
Grondin Markus Ackermann, Matthew Kerr, Ozlem Celik Peter den Hartog,
Richard Dubois, Seth Digel, Tobias Jogler, Toby Burnett, Tyrel Johnson,
and Yasunobu Uchiyama.

I would like to acknowledge the Stanford and SLAC administrators and
technical support: Glenn Morris, Stuart Marshall, Ken Zhou Martha Siegel,
Chris Hall, Ziba Mahdavi, Maria Frank, Elva Carbajal Violet Catindig.
They are awesome and really keep this place running!

I would like to acknowledge the large number of graduate students I
worked along side.  First, I acknowledge the Fermi Grad Students: Adam Van
Etten, Alex Drlica-Wagner, Alice Allafort, Bijan Berenji, Eric Wallace,
Herman Lee Keith Bechtol, Kyle Watters, Marshall Roth Michael Shaw, Ping
Wang, Romain Rousseau, Warit Mitthumsiri, and Yvonne Edmonds.  Second,
I acknowledge my graduate student peers at Stanford: Ahmed Ismail, Chris
Davis, Dan Riley, Joel Frederico, Joshua Cogan, Kristi Schneck, Kunal
Sahasrabuddhe, Kurt Barry, Mason Jiang Matthew Lewandowski Paul Simeon,
Sarah Stokes Kernasovskiy, Steven Ehlert, Tony Li, Yajie Yuan

I would like to acknowledge my parents Jim Lande and Joyce Mason as well
as my brother Nathan Lande. They put up with my moving three time zones
away from where I grew up. I would like to acknowledge my girlfriend
Helen Craig, who kept me sane as I put my thesis together.

I acknowledge the great help of my thesis committee: Elliott Bloom, Roger
Romani, Stefan Funk, Persis Drell, Brad Efron. Finally, I would like to
personally thank my thesis adviser Stefan Funk.  On many occasions, my
PhD research felt insurmountable and I doubted my abilities.  But even
when I felt lost, Stefan never gave up on me. He always encouraged me to
keep pushing forward, to keep learning, and to keep asking questions.
Stefan's faith in me never wavered, and he always made me want to
succeed. I hope that this thesis stands as a testament to his mentoring.
