\section{The \Acstitle{LAT} Instrument Response Functions}
\seclabel{lat_irfs}


The performance of the LAT is quantified by its effective area
and its dispersion. The effecive area represents the collection area of the
\ac{LAT} and the dispersion represents the probaility of misreconstructing
the true parameters of the incident $\gamma$-ray.

We will write the
effective area as $\effectivearea(\energy,\time,\solidangle)$.  It is a
function of energy, time, and \ac{SA} and is measured in units of area
($\cm^2$). The effective area is also a function of the conversion type
of the $\gamma$-ray (front-entering or back-entering event), and the azimuthal
angle of the $\gamma$-ray, but we will ignore these effects in what follows.

The dispersion is the probability of a photon with true energy
\energy and incoming direction $\solidangle$ at time \time being
reconstructed to to have an energy $\energy'$, an incomming direction
$\solidangle'$ at a time $\time'$.  The dispersion is written as
$\dispersion(\energy',\time',\solidangle'|\energy,\time,\solidangle)$.
It represents a probability and is therefore normalized such that
\begin{equation}
  \int \int \int \denergy \dsolidangle \dtime 
  \dispersion(\energy',\time',\solidangle'|\energy,\time,\solidangle) = 1
\end{equation}
Therefore,
$\dispersion(\energy',\time',\solidangle'|\energy,\time,\solidangle)$
has units of 1/energy/\acl{SA}/time


For LAT analysis, we conventionally make the simplifying assumption that
the energy, spatial, and temporal dispersion decouple:
\begin{equation}
  \dispersion(\energy',\time',\solidangle'|\energy,\time,\solidangle) = 
  \psf(\solidangle'|E,\solidangle) \edisp(\energy'|\energy) \tdisp(\time'|\time)
\end{equation}

Here, \psf is the point-spread function and represents \ldots
\todo[inline]{BETTER DISCUSSION OF PSF OF THE LAT, WHAT ITS SCALE IS\ldots}


Finally, we note that in principle, there is a finite timing
resolution of $\gamma$-rays measured by the \ac{LAT}. But
the timing accuracy is $<10\unitspace\microsecond$
\microsecond\cite{atwood_2009a_large-telescope} Since this is much
less than the smallest timing signal which is expected to be observed
by the \ac{LAT} (millisceond pulsars), issues with timing accuracy are
typically ignored.

For the \ac{LAT}, the effective area, \ac{PSF}, and energy dispersion
are discussed in \subsecref{Performance_lat}.

\edisp represents the energy dispersion of the LAT.
The energy dispersion of the LAT is a function of both the
incident energy and incident angle of the photon. It varies
from $\sim$ 5\% to 20\%, degrading at lower energies due to energy
losses in the tracker and at higher energy due to electromagnetic
shower losses outside the calorimiter. Similarly, it improves
for photons with higher incident angles that are 
allowed a longer path through the calorimieter \citep{ackermann_2012a_fermi-large}.



The convolution of the flux of a model with the instrument response 
produces the expected counts per unit energy/time/\acl{SA}
begin reconstructed to have 
an energy $\energy'$ 
at a position $\solidangle'$ and at a time $\time'$:
\begin{equation}
  \eqnlabel{eventrate}
  \eventrate(\energy',\solidangle',\time'|\modelparams)
  = \int \int \int \denergy \, \dsolidangle \, \dtime \,
  \fluxdensity(\energy,\time,\vec\Omega|\modelparams) \response(\energy',\solidangle',\time'|\energy,\solidangle,\time)
\end{equation}
Here, this integral is performed over all true energies, \acs{SA}, and times
for which the source model has support.



For sources with smoothly-varying spectra, the effects of ignoring
the inherent energy dispersion of the LAT are typically small.
\cite{ackermann_2012a_fermi-large} performed a monte carlo simulation to show
that for power-law point-like sources, the bias introduced by ignoring
energy dispersion was on the level of a few perect.  Therefore, energy
dispersion is typicially ignored for standard likelihood analysis:
\begin{equation}
\edisp = \delta(\energy-\energy')
\end{equation}
We cauation that for analysis of sources extended to energies below
$100\unitspace\mev$ and for sources expected to have spectra that do
not smoothly vary, the effects of energy dispersion could be more severe.

\begin{itemize}
  \item \todo{Why discard time dispersion}
\item \todo[inline]{WRITE ENERGY DISPERSION AS A DELTA FUNCTION}
\end{itemize}


\todo{FINISH}
Therefore, the instrument response is typically approximated as
\begin{equation}
  \response(\energy',\solidangle',\time'|\energy,\solidangle,) = 
  \effectivearea(\energy,\time',\solidangle) \psf(\solidangle'|E,\solidangle)
\end{equation}
The expected count rate is then typically integrated over time
to compute the total counts. Assuming that the source model
is time indepdendent, we get: 
\begin{equation}
  \eventrate(\energy',\solidangle'|\modelparams)
  = \int \dsolidangle \,
  \fluxdensity(\energy,\vec\Omega|\modelparams) 
\left(
\int \dtime \intspace \effectivearea(\energy,\time,\solidangle) 
\right)
\psf(\solidangle'|E,\solidangle)
\end{equation}
This equation essentially says that the counts expected by the LAT
for the particular model
is the product of the source's flux with the effective area and then
convolved with the point-spread function.

\todo[inline]{Figure out how the $\theta$ depedence of the IRFs factors into this calcualtion}







We assume that the effective area and the dispersion decouple and
we write the LAT's instrument response as
\begin{equation}
  \response(\energy',\solidangle',\time'|\energy,\solidangle,\time) = 
\effectivearea(\energy,\time,\solidangle) \dispersion(\energy',\time',\solidangle'|\energy,\time,\solidangle)
\end{equation}
Therefore, the instrument response has units of area/energy/\acl{SA}/time
