\chapter{Search for \Acsptitle{PWN} associated with \tev Pulsars}
\chaplabel{tevcat}

\paperref{This chapter is based the first part of the paper
  ``Constraints on the Galactic Population of TeV Pulsar Wind Nebulae using Fermi Large Area Telescope Observations''
  \citep{acero_2013a_constraints-galactic}.}

In \chapref{extended_search}, we searched for spatially-extended sources
in the 2FGL catalog.  This search showed that the spatial analysis
of \fermi sources is important in identifying $\gamma$-ray emitting
\acp{PWN}.  In that work, we analyzed the $\gamma$-ray emitting \acp{PWN}
\hessj{1825} and \mshfifteenfiftytwo which had previously been detected
in \ac{2FGL}.  In addition, this analysis discovered that there were three
additional spatially-extended \fermi sources coincident with \acp{PWN}
candidates (\hessj{1616}, \hessj{1632}, \hessj{1837}).

In \chapref{offpeak}, we then searched for $\gamma$-ray emitting \acp{PWN}
by looking in the off-peak emission of \ac{LAT}-detected pulsars. In
that analysis, we detected four $\gamma$-ray emitting \acp{PWN} (\velax,
the Crab Nebula, \mshfifteenfiftytwo, and \threecfiftyeight).

In this chapter, we continue our search for $\gamma$-ray emitting
\acp{PWN} by searching for \acp{PWN} which had previously been detected at
\ac{VHE} energies by \acp{IACT}. We note that the work presented here is a
very condensed version of the results presented in the accompanying work
\citep{acero_2013a_constraints-galactic}.  We refer to that publication
for a more detailed discussion of the analysis.

\section{Introduction}

We took all sources detected at \ac{VHE} energies and potentially
associated with \acp{PWN} and performed a search at \gev energies for
$\gamma$-ray emission. As was seen in previous chapters, many \acp{PWN}
have been detected both at \gev and \ac{VHE} energies. Therefore,
we suspect that by searching \ac{LAT} data in the regions of \ac{VHE}
\acp{PWN} might yield the discovery of new LAT-detecting \ac{PWN}.

In addition, there are several \ac{PWN} which have been detected at
\ac{VHE} energies which do not have an associated $\gamma$-ray pulsar
(such as \hessj{1825} and \hessj{1837}).  We therefore suspect that this
search strategy may discovery new \ac{PWN} which were not previously
discovered either in the off-peak search discussed in \chapref{offpeak}
or in other dedicated analyses.

\section{List of \ac{VHE} \Acstitle{PWN} Candidates}
\seclabel{tevcat_list_vhe_pwn_candidates}

\input{chapters/tevcat/tables/list_tev_sources}

We used \tevcat to define the our target list of \ac{VHE}
sources.  \tevcat is a catalog of sources detected at \ac{VHE}
energies by \acp{IACT}.\footnote{\tevcat can be found at
\url{http://tevcat.uchicago.edu}.}  We selected all sources from this
catalog where the emission was classified as being due to a \ac{PWN}. In
addition, we included all \ac{UNID} sources within 5\degree of the
galactic plane since they could be due to a \ac{PWN}.  Finally, we
included \hessj{1023}. Although this source is classified as a massive
star cluster in the \tevcat, \cite{de-naurois_2013a_galactic-h.e.s.s.}
suggested that the emission could be due to \ac{PWN}. The list of all
sources included in our analysis as well as their classification in
\tevcat can be found in \tabref{TeV_sources}.

\section{Analysis Method} \seclabel{tevcat_analysis_method}

In this search, our analysis method was very similar to the analysis in
\chapref{offpeak}. We used the same hybrid \pointlike/\gtlike approach
for studying the spatial and spectral character of each source and
modeled the region using the same standard background models.

The major difference was that this analysis was performed only for
$\energy>10\unitspace\gev$.  As can be seen in \chapref{offpeak}, for
energies much lower than $10\unitspace\gev$, source analysis becomes
strongly influenced by Galactic-diffuse emission and systematic errors
associated with incorrectly modeling the emission. On the other hand,
the $\gamma$-ray emission from \ac{PWN} is expected to be the rising
component of an \ac{IC} peak which falls at \ac{VHE} energies. Therefore,
the emission observed by the \ac{LAT} is expected to be hard and most
significant at higher energies. Therefore, we expect that starting the
analysis  at $10\unitspace\gev$ will significantly reduce systematics
associated with this analysis while preserving most of the space for
discovery.

Because the analysis was performed only in this high energy range where
the \ac{PSF} of the \ac{LAT} is much improved, we were able to use a
smaller region of interest (a radius of $5\degree$ in \pointlike and a
square of size $7\degree\times7\degree$ in \gtlike).

Another differences is that we used an event class with less
background contamination (Pass 7 Clean instead of Pass 7
Source) and modeled nearby background sources using \ac{1FHL}
\citep{ackermann_2013a_first-fermi-lat}.

For our analysis, we assume the \gev emission to have a power-law spectral
model and to have whatever was the published spatial model observed at
\ac{VHE} energies.  We define \tstev as the likelihood-ratio test for
the significance of the source assuming it to have the power-law spectral
model and the published \ac{VHE} spatial model.  We claim a detection when
$\tstev > 16$.  Our significance test has only two degrees of freedom:
the flux and spectral index.  Therefore, following Wilks' Theorem (see
\subsecref{monte_carlo_validation}), this corresponds to a $3.6\sigma$
detection threshold. When the source is significantly-detected, we quote
the best-fit spectral parameters and otherwise we derive a upper limit
on the flux of any potential emission.

We note that \cite{acero_2013a_constraints-galactic} performs a more
detailed morphological analysis which also fits the positions of the
sources assuming their emissions to be point-like and spatially-extended.
That work then uses \tsext (See \subsecref{extension_fitting}) to test
if the emission is spatially-extended and otherwise computes an upper
limit on any potential spatial extension.  The more detailed analysis in
\cite{acero_2013a_constraints-galactic} is needed to compare the spatial
overlap between the \gev and \ac{VHE} emission. But for brevity, we omit
the details and simply use the results.

We note that many of these \acp{PWN} candidates are in
regions with \ac{LAT}-detected pulsars.  For these sources,
\cite{acero_2013a_constraints-galactic} presents the spectral and spatial
results both with and without the \ac{LAT}-detected pulsar in the
background model. For the analysis, the spectrum of these background
pulsars was taken from the \ac{2FGL} catalog.  For simplicity, we
present only the analysis with the pulsar included in the background
model. This analysis presents our best-guess at the true spectrum of
any \ac{PWN} emission.  But we caution that this method could be biased
in either oversubtracting or undersubtracting the pulsar depending upon
systematics in the fit of the pulsar.

There are three major sources of systematic uncertainty
effect the spectrum of these sources. The first systematic
is due to uncertainty in our modeling of the Galactic diffuse
emission.  We estimate this uncertainty following the method of
\secref{systematic_errors_on_extension}.  The second systematic is due
to uncertainty in the effective area.  We estimated the systematic
using the method described in \cite{ackermann_2012a_fermi-large}.
The final systematic is due to our uncertainty in the true morphology of
of the source. We used as our systematic error on this the difference
in spectrum when the source is fit assuming the published \ac{VHE}
spatial model and when using the spatial model measured by the LAT.

\section{Sources Detected} \seclabel{tevcat_sources_detected}

\input{chapters/tevcat/tables/spatial_results}

We detected 22 sources.  For significantly-detected sources,
we present the spatial and spectral results for these sources in
\tabref{tevcat_spatial_spectral}.  Flux upper limits for non-detected
sources as well as spectral points in three independent energy bins are
can be found in \cite{acero_2013a_constraints-galactic}.

We attempt to classify the \gev emission into four categories:
\PWNClass-type for sources where the \gev emission is clearly identified
\ac{PWN}, \PWNcClass for sources where the \gev emission could potentially
be due to a \ac{PWN}, \PSRClass-type for sources where the emission is
most likely due to pulsed emission inside the pulsar's magnetosphere,
and \OtherClass-type (for other) when the true nature of emission is
uncertain.

We categorize a source as \PWNClass-type or \PWNcClass-type when the
emission has a hard spectrum which connects spectrally to the \ac{VHE}
spectrum and when there is some multiwavelength evidence that the
\gev and \ac{VHE} emission should be due to a pulsar-wind nebula.
We label a source as \PWNClass-type when the \ac{VHE} emission suggests
more strongly that the emission is due to a \ac{PWN}.  We include
in \tabref{tevcat_spatial_spectral} the source classifications
for each source.  We will discuss the \PWNClass-type source in
\subsecref{pwn_pwnc_sources}.

\subsection{\PWNClass-type and \PWNcClass-type Sources}
\subseclabel{pwn_pwnc_sources}

In total, we detect fourteen sources which we classify as \PWNClass-type
or \PWNcClass-type. Five of these \ac{PWN} and \ac{PWN} candidates are
first reported in this analysis.

Of these fourteen sources, three are classified as \PWNClass-type.  They
are \hessj{1356}, \mshfifteenfiftytwo (\hessj{1514}), and \hessj{1825}.
\hessj{1356} and \mshfifteenfiftytwo are classified as \PWNClass-type
because of the correlation between the X-ray and \ac{VHE} emission
\citep{h.e.s.s.collaboration_2011a_discovery-source,aharonian_2005a_discovery-extended}.
\hessj{1825} is classified as \PWNClass-type because of
the energy-dependent morphology observed at \ac{VHE} energies
\citep{aharonian_2006a_energy-dependent}.  We note that \hessj{1356}
was first presented as an \ac{PWN} in this work.  Once we add the Crab
Nebula and \velax (not analyzed in this work) to this list, the total
number of clearly-identified \acp{PWN} detected at \gev energies is five.

In addition, we detect eleven \PWNcClass-type sources.  Four of these
sources are first reported in this work: \hessj{1119}, \hessj{1303},
\hessj{1420}, and \hessj{1841}.  These sources are all powered by
pulsars energetic enough to power the observed emission (\psrj{1119},
\psrj{1301}, \psrj{1420}, \psrj{1838}), and they all have a hard
spectrum which connects to the spectra observed at \ac{VHE} energies.  The
multiwavelength interpretation of the new \ac{PWN} and \ac{PWN} candidates
is discussed more thoroughly in \cite{acero_2013a_constraints-galactic}.

We mention that three of these \PWNcClass-type sources have LAT-detected
pulsars (\psrj{1119}, \psrj{1420}, and \psrj{1838}) and therefore were
studied in \chapref{offpeak}.

In \chapref{offpeak}, \psrj{1119} has $\ts=61.3$ and is classified as a
``U''-type source because the spectrum is relatively soft (spectral index
$\sim2.2$).  But the spectra of this source shows both a low-energy
component and high-energy component.  So most-likely, the off-peak
emission is composite of the pulsar at low energy and the \ac{PWN}
at high energy.

For \psrj{1420}, the off-peak emission (at the position of the pulsar)
has $\tspoint=8.1$ which is significantly less then the emission observed
in the high-energy analysis (\tstev=36).  It is possible that for this
source, \tstev is being overestimated by undersubtracting the emission
of \psrj{1420}.

Finally, \psrj{1838} is significantly detected in the off-peak,
but as a soft and significantly-cutoff spectrum. This emission
is also spatially-extended and when the emission is assumed to be
spatially-extended, the extension expands incorporates both the emission
at the position of \psrj{1838} and also residual towards the center of
\hessj{1841}. So most likely, the off-peak region of \psrj{1838} shows
both a magnetospheric component at the position of the pulsar as well
as the emission of \hessj{1841} observed for $E>10\unitspace\gev$.

The remaining seven sources have been previously published:
\hessj{1023} \citep{ackermann_2011a_fermi-lat-search},
\hessj{1640} \citep{slane_2010a_fermi-detection}, \hessj{1616}
\citep{lande_2012_search-spatially}, \hessj{1632}
\citep{lande_2012_search-spatially}, \hessj{1837}
\citep{lande_2012_search-spatially}, \hessj{1848}
\citep{tam_2010a_search-counterparts}, and \hessj{1857}
\citep{rousseau_2012a_fermi-lat-constraints}.  We mention that we
classify \hessj{1848} as \PWNcClass even though the \gev emission has
a soft spectrum because of the careful multiwavelength considerations
presented in \cite{lemoine-goumard_2011a_fermi-lat-detection}.

\subsection{\OtherClass-type Sources}

We detect six \OtherClass-type sources.  Two of these sources
(\hessj{1634} and \hessj{1804}) have a hard spectrum which connects
spectrally to the \ac{VHE} emission, but are not classified as \ac{PWN}
based upon multiwavelength considerations.  For \hessj{1634}, is not
a \ac{PWN} candidate because there are no pulsar counterparts able to
power it.  Finally, \hessj{1804} is was suggested to be SNR G8.7$-$0.1
(W30) \citep{ajello_2012a_fermi-large}.

The remaining four \OtherClass-type sources have a soft spectrum
which does not connect with the \ac{VHE} emission: \hessj{1018},
\hessj{1507}, \hessj{1834}, and \verj{2016}.  \hessj{1018}
is in the region of the $\gamma$-ray binary \onefglj{1018.6}
\citep{the-fermi-lat-collaboration_2012a_periodic-emission} and also
\snrg{284.3}.  \gev emission from the region of \hessj{1507} is also
studied in \cite{domainko_2012a_exploring-nature}.  \hessj{1834} and
\verj{2016} both lack pulsars energetic enough to power the observed
emission.

\subsection{\PSRClass-type Sources}

In \citep{acero_2013a_constraints-galactic}, the
$\energy>10\unitspace\gev$ search for \ac{PWN} was performed both with
and without associated pulsars included in the background model.  When
associated \ac{LAT}-detected pulsars were not included in the background
model, we detected nine sources which were consistent with magnetospheric
emission.  After modeling the associated pulsars in the background, only
\hessj{1708} remained significant.  Even so, we the source is so strongly
influenced by the inclusion of the pulsar in the background model, so
we suspect that the emission is entirely magnetospheric and that our
pulsar emission model underpredicts the true magnetospheric emission.
