\section{Off-peak Analysis Method}
\seclabel{off_peak_analysis}

Characterizing both the spatial and spectral
characteristics of any off-peak emission helps discern its origin.
We employ a somewhat different analysis procedure here than
for the phase-averaged analysis described in \secref{spectralMethodSection}.  To evaluate the spatial characteristics of
any off-peak emission we use the likelihood fitting package \pointlike
\citep[detailed in][]{lande_2012_search-spatially}, and
to fit the spectrum we use \gtlike in binned mode via {\it pyLikelihood} as was done for the
phase-averaged analysis.

For each pulsar we start from
the same temporal and spatial event selections described in 
\secref{obsvSection} but we increase the maximum energy to 400 GeV (the
highest event energy for any ROI under this selection is $\sim$316 GeV).
For the \pointlike analysis we further select a 10$\degree$ radius ROI
and for \gtlike a $14\degree\times14\degree$ square ROI, both centered
on the pulsar postition.  Finally, we only consider photons with 
pulse phases within the corresponding off-peak interval.

We search for off-peak emission
assuming a point source and (except for the Crab Nebula and Vela-X, described below) 
a power-law spectral model.  We fit the position of this
putative off-peak source using \pointlike as described by \citet{nolan_2012_fermi-large}
and then use the best-fit position in a spectral analysis with \gtlike.
From the spectral analysis we require $TS\geq25$ (just over $4\sigma$)
to claim a detection.  If $TS<25$, we compute upper limits on the flux 
in the energy range from 100 \mev to 316 \gev
assuming
a power law with photon index fixed to 2.0 and a PLEC1 model with
$\Gamma=1.7$ and $E_{\rm cut}=3$ GeV.

The spectrum of the Crab Nebula (associated with PSR J0534+2200) is
uniquely challenging because the GeV spectrum contains both a falling
synchrotron and a rising inverse Compton component \citep{abdo_2010a_fermi-large}.
For this particular source we used the best-fit two-component spectral
model from \cite{buehler_2012a_gamma-ray-activity} and fit only the overall
normalization of the source. 
In addition, for Vela-X (associated with PSR J0835-4510) we took the
best-fit spectral model from \cite{grondin_2013a_vela-x-pulsar} and fit only the overall
normalization of this source. This spectrum has a smoothly broken power
law spectral model and was fit assuming Vela-X to have an elliptical
disk spatial model.

If the off-peak source is significant, we test whether the spectrum shows
evidence for a cutoff, as described in \secref{spectralMethodSection}
and by \citet{ackermann_2011a_fermi-lat-search}, assuming the source is at
the pulsar position.  We say that the off-peak emission shows evidence for
a cutoff if $TS_{\rm cut}\geq9$, corresponding to a $3\sigma$ detection.

For a significant off-peak point source,
we use \pointlike to test if the emission is significantly
extended.  We assume a radially-symmetric Gaussian source
and fit the position and extension parameter ($\sigma$) as described
in \citet{lande_2012_search-spatially}.  The best-fit
extended source parameters are then given to \gtlike, which is used
to fit the spectral parameters and the significance of the extension
over a point source, $TS_{\rm ext}$, evaluated as described in
\citet{lande_2012_search-spatially}.  
That paper established that $TS_{\rm ext}\geq16$ means highly probable source extension.
In the present work we aim only to flag possible extension, and use  $TS_{\rm ext}\geq9$.
%% 
%% We say that the off-peak emission shows evidence for extension if $TS_{\rm ext}\geq16$.

To test for variability, even without significant emission over the 3-year time
range, we divide the dataset into 36 intervals and fit the point-source
flux independently in each interval, 
computing $TS_{\rm var}$ as in 2FGL.  
For sources with potential magnetospheric off-peak emission and for
regions with no detection, we performed the test at the pulsar's position.
Otherwise, we test at the best-fit position.
The off-peak emission is said
to show evidence for variability if $TS_{\rm var}\geq91.7$, corresponding
to a $4\sigma$ significance.  
%
As noted in \secref{obsvSection}, our timing solutions for PSRs J0205+6449 and J1838$-$0537 are not  
coherent across all three years.  
For these two pulsars, we excluded the time ranges without ephemerides  
and only tested for variability during months that were completely covered.  
For J1838$-$0537 only one month is lost, whereas for J0205+6449 the 7\% data loss is spread across
three separate months.
As a result, $TS_{\rm var}$ for these pulsars is a conservative estimate of variability significance.

The procedure described above, especially the extension analysis,
is particularly sensitive to sources not included in 2FGL that are near the pulsar of interest,
for two reasons.
First, we are using an additional year of data and second,
when ``turning off'' a bright pulsar nearby, faint sources become more
important to the global fit.  Therefore, in many situations we had to run
the analysis several times, iteratively improving the model by including
new sources, until we removed all $TS>25$ residuals. The final
\gtlike-formatted XML source model for each off-peak 
region is included in the auxiliary material.

There are still, however, pulsars for which we were unable to obtain
an unbiased fit of the off-peak emission,
most likely due to inaccuracies in the model of the Galactic diffuse emission
and incorrectly modeled nearby sources.  The most common symptom
of a biased fit is an unphysically large extension.  In these cases,
the extended source attempts to account for multiple point sources or
incorrectly-modeled diffuse emission,
not just the putative off-peak emission.  Systematics associated
with modeling extended sources are discussed more thoroughly in
\citet{lande_2012_search-spatially}.  For the purposes of this
catalog, we have flagged the pulsars where off-peak analysis suffered from
these issues and do not attempt a complete understanding of the emission.

Observations of magnetospheric off-peak emission can be used to 
constrain pulsar geometry. Therefore, it is important to know if 
off-peak emission that is otherwise pulsar-like might instead
be incorrectly-modeled Galactic diffuse emission. 
We therefore performed a limited study of the systematics
associated with our model of the Galactic diffuse emission.

For sources which otherwise would be classified as magnetospheric, we
tested the significance of the emission assuming eight different
Galactic diffuse emission models as described in \citet{de-palma_2013a_method-exploring}. 
These models were constructed using a different model building strategy,
vary parameters of the Galactic diffuse emission model, and
have additional degrees of freedom in the fit.

We define $\tsaltdiff$ as the minimum test statistic of any of the
eight alternate diffuse models. This test statistic is computed
assuming the emission to be pointlike at the best-fit position
and is therefore comparable to \tspoint.
For sources which would otherwise be considered magnetospheric,
we flag the emission as potentially 
spurious if $\tsaltdiff<25$.
We caution that although this test can help to 
flag problematic regions,
these models do not probe the entirety of the uncertainty
associated with our model of the Galactic diffuse emission.
Therefore, some diffuse emission could still be incorrectly classified
as magnetospheric.

