\section{Off-Peak Individual Source Discussion}
\seclabel{off_peak_individual_source_discussion}

Here we discuss several interesting sources found in the off-peak analysis.

The off-peak emission from PSR J0007+7303 in the SNR CTA1 was previously
studied by \cite{abdo_2012a_j00077303-supernova}.  They found a soft and
not-significantly cut off source in the off-peak region that is marginally
extended.  We find a similar spectrum and extension significance ($TS_{\rm
ext}=10.8$), and therefore classify this source as type `U'.

The new type `W' source is associated with PSR J0205+6449
\citep{abdo_2009a_discovery-pulsations}.  The off-peak spectrum for this
source is shown in panel b of \figref{off_peak_seds}.  The emission
is best fit as a point source at $(l,b)=(130\fdg73,3\fdg11)$ with a
95\% confidence-level radius of $0\fdg03$.  The source has a hard
spectrum (power law with $\Gamma=1.61\pm0.21$) and is therefore
consistent with a PWN hypothesis.  This nebula has been observed
at infrared \citep{slane_2008a_infrared-detection} and X-ray
\citep{slane_2004a_constraints-structure} energies. This suggests
that we could be observing the inverse Compton emission from the same
electrons powering synchrotron emission at lower energies.  The PWN
hypothesis is supported by the associated pulsar's very high $\dot
E=2.6\times10^{36}$ erg s$^{-1}$ and relatively young characteristic
age, $\tau_c = 5400$ yr. This is consistent with the properties of
other pulsars with LAT-detected PWN, and we favor a PWN interpretation.
We note that the discrepancy between our spectrum and the upper limit
quoted in \citet{ackermann_2011a_fermi-lat-search} is mainly caused by
our expanded energy range and because the flux upper limit was computed
assuming a different spectral index.

However, we note that PSR J0205+6449 is associated to the
SNR 3C58 (G130.7+3.1).  Given the 2 kpc distance estimate from
\cite{abdo_2013a_second-fermi} and the density of thermal material estimated by
\cite{slane_2004a_constraints-structure}, we can estimate the energetics
required for the LAT emission to originate in the SNR.  Following the
prescription in \cite{drury_1994a_gamma-ray-visibility}, we assume the
LAT emission to be hadronic and estimate a cosmic-ray efficiency for the
SNR of $\sim10$\%, which is energetically allowed.  We therefore cannot
rule out the SNR hypothesis.

No TeV detection of this source has been reported, but given the hard
photon index at GeV energies this is a good candidate for observations
by an atmospheric Cherenkov telescope. Improved spectral and spatial
observations at TeV energies might help to uniquely classify the emission.

We obtain a flux for Vela-X which is $\sim10\%$ larger than the flux
obtained in \cite{grondin_2013a_vela-x-pulsar}. This discrepancy is
most-likey due to assuming a different spatial model for the emission
(radially-symmetric Gaussian compared to elliptical Gaussian).

PSR J1023$-$5746 is associated with the TeV PWN HESS J1023$-$575
\citep{aharonian_2007a_detection-extended}.  LAT emission from this
PWN was first reported in \citet{ackermann_2011a_fermi-lat-search}.
Because of the dominant low-energy magnetospheric emission, we
classify this as type `M' and not as a PWN.  A phase-averaged
analysis of this source for energies above 10 GeV is reported in
\citet{acero_2013a_constraints-galactic}.

PSR J1119$-$6127 \citep{parent_2011a_observations-energetic}
is associated with the TeV source HESS J1119$-$614\footnote{The
discovery of HESS J1119$-$614 was presented at the ``Supernova
Remnants and Pulsar Wind Nebulae in the Chandra Era'' in 2009. See
\url{http://cxc.harvard.edu/cdo/snr09/pres/DjannatiAtai\_Arache\_
v2.pdf}.}. Our off-peak analysis classifies this source as `U' because
its spectrum is soft and not significantly cut off. However, the SED
appears to represent a cutoff spectrum at low energy and a hard rising
spectrum at high energy.  \citet{acero_2013a_constraints-galactic}
significantly detect this PWN using the analysis procedure as described
for J1023$-$575.  We are likely detecting a composite of magnetospheric
emission at low energy and pulsar-wind emission at high energy.

PSR J1357$-$6429 \citep{lemoine-goumard_2011a_discovery-gamma-}
has an associated PWN HESS J1356$-$645 detected at TeV energies
\citep{h.e.s.s.collaboration_2011a_discovery-source}.  Our analysis
of the off-peak regions surrounding PSR J1357$-$6429 shows a source
positionally and spectrally consistent with HESS J1356$-$645,
but with significance just below detection threshold ($TS=21.0$).
\citet{acero_2013a_constraints-galactic} present significant emission
from this source.

The off-peak region of PSR J1410$-$6132
\citep{obrien_2008a_j1410-6132:-young} shows a relatively hard spectral
index of $1.90\pm0.15$, and the spectrum is not significantly cut off.
There is no associated TeV PWN and enough low-energy GeV emission is
present to caution against a clear PWN interpretation.  We classify this
source as `U', but further observations could reveal interesting emission.

PSR J2021+4026 is spatially coincident with the LAT-detected and spatially
extended Gamma Cygni SNR \citep{lande_2012_search-spatially}.
The off-peak emission from this pulsar is consistent with an
exponentially-cutoff spectrum and is therefore classified as type `M'.
The source's marginal extension ($TS_{\rm ext}=8.7$) is likely due to
some contamination from the SNR.

